Relative parabolic factorizations of Chevalley groups

### 2015-09-07 dennis-vaserstein.tex
Moved symplectic case into a separate lemma

Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
In the case $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
In the case $\Phi=\rB_\ell$ (resp. $\Phi=\rC_\ell$) the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ (resp. $\U(\Sigma_s^{+<}, R) \subseteq N_{rs}$)
and a separate argument is needed for the root subgroup corresponding to the sole short (resp. long) root of $\Sigma_s^+$.

Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
\begin{align*} \label{rel:CCF-specBC}
& x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2), \\
& x_{1,-1}(-ab^2) = x_{-2,1}(ab) \cdot [x_{-2, 2}(a), x_{2, -1}(b)].
\end{align*}
Clearly, the root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In fact, in view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$
\[ gA_{rs} \subseteq g {A_{rs}}^g = A_rs g = A_rs. \]
Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
Indeed, from the identity $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$

%TODO: finish proof of the theorem
\end{proof}

>>>>

Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
In the case $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
In the case $\Phi=\rB_\ell$ the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate argument is needed for the root subgroup corresponding to the sole short root of $\Sigma_s^+$.
Specializing identity~\eqref{rel:CCF} we get:
\begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
The root subgroup $X_{2, 0}(R)$ is contained in $\E(\Delta_s, R) \subseteq N_{rs}$.
On the other hand, by the above argument we know that $X_{1,-2}(R) \subseteq N_{rs}$, therefore $X_{1,0}(R) \subseteq N_{rs}$ and $\U(\Sigma_s, R) \subseteq N_{rs}$.
The case $\Phi=\rC_\ell$ will be analyzed separately below (see~\cref{lemma:DVcaseCl}).

Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
In fact, in view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$ one has
\[ gA_{rs} \subseteq g {A_{rs}}^g = A_rs g = A_rs. \]
Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
whence the statement of the theorem follows. \end{proof}

\begin{lemma} \label{lemma:DVcaseCl}

\end{lemma}
